Outstanding Title

### 2017-06-11 writing/EpiDraft.Rmd
Work on poster.

In `eesim`, the function `power_calc` can be used to investigate the effects of various sample sizes or relative risks on power. This function requires arguments including the parameter to be varied (sample size or relative risk), the desired values of that parameter, and lists of the same arguments as used in the `eesim` function. The `power_calc` function outputs a table of the values of the varied parameter along with their corresponding power. 
Here is an example of using `power_calc` to test power for different sample sizes:

@@

```{r}
power_calc(varying="average_outcome", values = c())
```

>>>>

In `eesim`, the function `power_calc` can be used to investigate the effects of various sample sizes, relative risks, or average outcome values on power. This function requires arguments including the parameter to be varied (sample size, relative risk, or average outcome), the desired values of that parameter, and lists of the same arguments as used in the `eesim` function. The `power_calc` function outputs a table of the values of the varied parameter along with their corresponding power. 
Here is an example of using `power_calc` to test power for different sample sizes:

@@

```{r}
power_calc(varying="average_outcome", values = c(.5, .75, 1, 2, 5), n=3650, n_reps=10, rr=1.1, exposure_type = "binary", central = c(0.048, 0.035, 0.046, 0.036, 0.035, 0.055, 0.053, 0.067, 0.070, 0.053, 0.033, 0.067), exposure_trend = "monthly", exposure_amp = .05, cust_base_func = custbase, cust_base_args = list(n1=1095, n2=2555, slope1=1.5, slope2=-.8, amp1=.5, amp2=.7),  custom_model = spline_mod, plot=TRUE)
```
